### 2013-11-15 tests_Housing.Rmd
organized article references
minot stuff

source("gapolyfuncs.R")
report <- test.regularization(my.data, population=30, iterations=25, lambda=0.8, runs=5)

@@

########################################################
# check what attributes Random Forest select has the most importants

>>>>

source("gapolyfuncs.R")
report <- test.regularization(my.data, population=300, iterations=100, lambda=0.8, runs=25)

@@

########################################################
# check what attributes Random Forest select as the most importants
